Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-07-09 PAPER/main.tex
added authorrunning

\documentclass[oribibl]{llncs}
\input{includes/preamble.tex}

@@

\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\maketitle

@@

Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}. It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.

>>>>

\documentclass[oribibl, runningheads]{llncs}
\input{includes/preamble.tex}

@@

\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\authorrunning{A. L. Hawa et al.}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\maketitle

@@

Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.} It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.
